\documentclass[10pt,a4paper,sans,english]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
\usepackage{comment}
\usepackage{multicol} % Add this line to the preamble

% ...
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Gathu }
\familyname{Macharia}
\title{Actuary \& Data Scientist}                               % optional, remove/comment the line if not wanted
\address{Nyeri-Mweiga Road}{P.o Box 657-10100 Nyei}{Kenya}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty
\mobile{+254702 499 673}                          % optional, remove/comment the line if not wanted
%\phone{phone number}                           % optional, remove/comment the line if not wanted
                            % optional, remove/comment the line if not wanted
\email{sgathuh@gmail.com}                               % optional, remove/comment the line if not wanted
\homepage{gathuh.github.io/website/}                         % optional, remove/comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove/comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{A theory has only the alternative of being right or wrong. A model has a third probability: it may be right, but irrelevant\\
\textit{\textbf{Gathu Simon Macharia}}}                                % optional, remove/comment the line if not wanted
\social[linkedin]{gathu-simon-82a275199/}
\social[github]{Gathuh}
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Education}
\cventry{2025-- 2026}{Full Stack Developer \& Data Scientist}{ALX }{}{}{ }
\cventry{2021--2024}{Bsc Statistics and Actuarial Science}{Dedan Kimathi University of Technology}{Nyeri}{}{Statistics Background and Statistical Modeling using R and Python}  % arguments 3 to 6 can be left empty
\cventry{2024}{Data Science Summer School and Workshop}{Data Science Africa Africa}{Nyeri}{}{Data science for social good,Computer Vision Data collection, extraction of features and modeling}
\cventry{2021--2021}{Cisco Certified Network Association}{Jomo Kenyatta University of agricullture and Technology}{Kiambu}{}{Basic Networking and Network Visualization}

\cventry{2016--2019}{Certificate of Secondary Education Kenya}{Utumishi Academuy}{Gilgil}{}{Secondary certificate and Computer background}


\section{Degree thesis}
\cvitem{title}{Modeling the Recovery Time of Stock Prices using Accelerated Failure Time Model}
\cvitem{supervisors}{Dr. Mundia}
\cvitem{description}{Using statistical survival models to model the survival time of medical condition to be prevelant is widely used by medical researchers. We thought of using the same concep but this time to assess the effects of covariates on recovery time of stocks in Kenyan stocks. The hazard rates were not proportional so we opted for non proportion hazard model which is AFT}
\section{Experience}

\subsection{Internship}
\cventry{2024--2024}{Data Scientist }{Info Tech}{Remote}{}{Machine Learning Projects and Data preprocessing  }
\cventry{2023--204}{Risk Management and Internal Audit}{National Social Security Fund}{Nairobi}{}{Utilized Benfords law in fraud detection. Used IDEA software, R  and Excel to analyze Audit data. Also made compliance files and was involved in writing reports of respective field.}
\subsection{Job}
\cventry{2022--Present}{Freelance}{Freelancer}{Fivver \& Upwork}{}{Used both R, SPSS and Python to carry out test of hypothesis, generalized models, Bayesian models, Gradient Boosting Models, Neural Networks,PCA and others.}



\section{Languages}
\cvitemwithcomment{Kiswahili}{Proficient}{Favourite} 
\cvitemwithcomment{English}{Proficient}{Reading}
\cvitemwithcomment{Gikuyu}{Proficient}{Lingual}
\section{Skills}
\cvdoubleitem{Actuarial Theory}{Insurance, Investment and Banking theory}{}{}
\cvdoubleitem{Big Data}{Apache Spark, Hardoop, Bigmemory and ff}{}{}
\cvdoubleitem{R}{Proficient in statistical Programming}{Proficient}{Data Modeling \&  Visualization}
\cvdoubleitem{Python}{Proficient in Machine learning}{Good}{Web scrapping}
\cvdoubleitem{SPSS}{Statistical Inferencing}{ }{}
\cvdoubleitem{EXCEL}{Data Analysis}{}{}


\section{Projects}
\cvlistitem{Used GIS Mapping to visualize the population Density of Kenya in each Sub-county  in Python; A heatmap as the output} {}
\cvlistitem{Used Decision Trees, Logistic Regression and Neural Network to recommend loan approval or loan denial on
	loan applications from customers in SPSS } {}

\cvlistitem{PCA Used principal Component Analysis for Dimension Reducability in R , prcomp()}

\cvlistitem{Forecasting the stock prices of NSE-listed Companies using GARCH Extensions.}

\cvlistitem{Built a predictive model using logistic regression to estimate the probability of customer churn.}{and alot more ...}

\section{Extra Curricular Activities}
\cvlistitem{Member f Data Science Africa}
\cvlistitem{Participated in 2021 Nationals at UON and emerged as winners.}{}
\cvlistitem{Actuarial Club}
\cvlistitem{Data Science Society DSAIC   (R Tutor) }








\vspace{0.5cm}

\section{References}
\begin{multicols}{2} % Start two-column layout
	\textbf{Name:} Dr. Mundia S.M, Lecturer\\
	\textbf{Position:} Project Coordinator\\
	\textbf{Company:} Dedan Kimathi University of Technology \\
	\textbf{Contact:} +254 721 302 869\\
	\textbf{Email:} simon.maina@dkut.ac.ke \\
	
	\vspace{0.5cm} % Add some vertical space between entries
	
	\textbf{Name:} Julius Miheso \\
	\textbf{Position:} Internal Auditor \\
	\textbf{Company:} NSSF \\
	\textbf{Contact:} +254 720 652 682 \\
	\textbf{Email:} atsiaya80@gmail.com \\
	
	\columnbreak % Switch to the second column
	
	\phantom{Placeholder text} % Creates invisible space equivalent to this text
	\vspace{6\baselineskip} % Creates space for a missing referee
	
	\textbf{Name:} Gideon Ngome \\
	\textbf{Position:} Risk Manager \\
	\textbf{Company:} NSSF \\
	\textbf{Contact:} +254 746 595 822 \\
	\textbf{Email:} ngomegideon@yahoo.com \\
\end{multicols} % End two-column layout


\end{document}
